---
title: "Using wrviz"
author: "Timothy Adams"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using wrviz}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

wrviz is a simple package, designed to easily create climate heatmaps. 

```{r}
library(wrviz)

df <- expand.grid(temp=0:8,precip=seq(0.7,1.3,by=0.1))
df$rel <- seq(40,100,length=63)

climate_heatmap(df,"rel",80)
climate_heatmap(df,"reliability", binary = FALSE, metricCol = "rel")
```


## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```
